\documentclass[5pt]{resume}
\usepackage{pifont}
\usepackage[left=0.2in,top=0.2in,right=0.2in,bottom=0.2in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}


% Adjust global spacing for lists
\setlist{noitemsep, topsep=-3pt, parsep=0pt, partopsep=0pt}

% Hyperlink styling
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}


\name{Osbaldo Arellano}
\address{arellano@oregonstate.edu \textbar\ (503) 877-7203}
\address{\href{https://www.linkedin.com/in/osbaldoarellano}{linkedin.com/in/osbaldoarellano} \textbar\ \href{https://blogs.oregonstate.edu/ozzythecomputerguy/}{blogs.oregonstate.edu/ozzythecomputerguy}}

\begin{document}


\begin{rSection}{Education}
    \item \textbf{Oregon State University} \textbar\ Computer Science, Cybersecurity Focus \hfill 2021-2025
\end{rSection}

\begin{rSection}{Relevant Coursework}

    \item \textbf{Cryptography (CS 427)}, \textbf{Computer Networks (CS 372)}, \textbf{Computer Networks (CS 372)}
   \item \textbf{Operating Systems I \& II (CS 374, CS 444):} Developed complex OS components in C, including a custom shell for process management, OTP encryption, memory translation, and socket programming. Extended JOS with a custom bootloader in assembly, user-space programs, breakpoints, memory management, hardware API integration, and concurrent process handling.
\end{rSection}

\begin{rSection}{Work Experience}
    \item \textbf{Internship Ambassador} \textbar\ The Script (The Contingent) \textbar\ Oregon State University \hfill Oct. 2024 - Present 
    \begin{itemize}[leftmargin=0.15in] \item Responsible for recruiting BIPOC students into The Script’s internship program through strategic outreach and collaboration with university departments and student organizations.
    \end{itemize}
    \item \textbf{DevOps Engineer Intern (Two Summer Internships)} \textbar\ Trimble \textbar\ Portland, OR (Remote) \hfill Jun. 2023 - Sep. 2024
    \begin{itemize}[leftmargin=0.15in]
        \item \textbf{Technology stack:} \textit{C\#, Azure DevOps, Azure Portal, Azure Pipelines, SQL Server, PowerShell, Kubernetes.}
         \item  Automated the deployment and configuration of Windows 11 environments using C\# within the Infrastructure as Code (IaC) app, installing Vista Viewpoint Construction software, security applications, and .NET environment setup for provisioning on Azure VMs. 
         \item Developed an Azure Pipeline to dynamically retrieve VMs for colleagues in India and configure their local SQL environment based on their work location (local or remote). Implemented SQL and PowerShell scripts to adjust directory paths in database entries, resolving issues caused by environment-specific path mismatches.
    \end{itemize}

    \item \textbf{Software Engineer (University-Sponsored Internship)} \textbar\ Sports Betting Startup (Remote) \hfill Sep. 2023 - Jun. 2024
    \begin{itemize}[leftmargin=0.15in]
        \item \textbf{Technology stack:} \textit{Go, Angular, Docker, AWS Lambda, AWS RDS, GitHub Actions.}
        \item Architected the CI/CD pipeline and backend infrastructure in Go using GitHub and AWS services.
        \item Integrated front-end components with Angular and optimized CSS for responsive design, ensuring a mobile-first experience.
    \end{itemize}

    \item \textbf{HRIS Backend Software Engineer Intern} \textbar\ Trimble  \textbar\ Portland, OR (Remote) \hfill Jun. 2022 - Sep. 2022
    \begin{itemize}[leftmargin=0.15in]
        \item \textbf{Technology stack:} .NET, Angular, SQL Server, Docker, Azure.
        \item Developed an auditing system for HR administrators to view historical changes, improving data traceability.
        \item Implemented pagination in RESTful APIs to efficiently handle large data sets, improving performance for HR operations.
    \end{itemize}

    
\end{rSection}

\begin{rSection}{Personal Projects}
    \item \textbf{BlueLifeLabor.com} \textbar\ Netlify, JavaScript, HTML, CSS, Bootstrap
    \begin{itemize}[leftmargin=0.15in]
        \item Designed, developed, and deployed a responsive mobile-first website for a business with 80 employees. 
        \item Worked closely with client to identify project requirements, and successfully delivered all requirements. 
    \end{itemize}
    \item \textbf{Kubernetes Platform} \textbar\ Azure AKS, Terraform
    \begin{itemize}[leftmargin=0.15in]
        \item Deployed a cloud platform using Azure AKS with Terraform, establishing a secure and scalable Kubernetes environment.
    \end{itemize}

\end{rSection}  
\begin{rSection}{Clubs and Awards}
    \item \textbf{Society of Hispanic Professional Engineers}, \textbf{U.S Hispanic Leadership Conference Oregon representative.}
\end{rSection}

\end{document}
